The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-04-04 paper.tex
preliminary finish of Chris suggestions

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}
\usepackage{enumitem}

@@

\newcommand{\Sers}{S\'{e}rsic }
\newcommand{\Lagr}{\mathcal{L}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: ojamesturner@icloud.com (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes? 
\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}

This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work. \\

@@

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
Predominantly, the galaxies were originally selected for spectroscopic follow-up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).

@@

Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$, {\it HK}-band $R\simeq2000$).
\subsubsection{Observations}\label{subsubsec:Obs}

@@

To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, facilitating both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the {\it K}-band greatly reduces the sky-line residuals. 
We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
The PSF was determined from fitting the {\it K}-band collapsed, stacked standard-star cube in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack. \\

@@

To measure $R_{1/2}$ for the galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening. \\

@@

\begin{enumerate}[label=(\roman*)] \item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
\item $\frac{S}{N_{m}} > 3$
\end{enumerate}

@@

The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
The 32/38 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.

@@

Throughout the following sections we analyse the derived kinematic parameters of the isolated field sample, placing the galaxies in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
In Appendix \ref{app:comparison_samples} we also describe the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
    \end{subfigure} \hspace{0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{v_evolution.png}
    \end{subfigure}
    \caption{{\it Left:} We plot log($V_{C}$) vs. log($M_{\star}/M_{\odot}$) for the isolated field sample, with the rotation-dominated galaxies in red and dispersion-dominated galaxies with the hollow symbols.
    We also plot with the solid green line the $z\simeq0.9$ relation recovered from a fit to $\simeq400$ rotation-dominated galaxies from the KROSS survey \protect\cite{Harrison2017}, with the shaded region showing the associated $\simeq$0.2 dex scatter on the fit.
    This $z\simeq0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
    The rotation-dominated KDS galaxies, and galaxies classed as reliable from the AMAZE survey \protect\citep{Gnerucci2011}, also show no evolution from this relation within the scatter, with the dispersion-dominated galaxies scattering below the relation.
    This highlights the need for careful sample selection when constructing this relation.
    {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors.
    The mean mass of each survey is listed beside the survey name.
    The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion-dominated galaxies with lower rotation velocities.}
    \label{fig:tf_relation}
\end{figure*}

@@

@@

We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a_{z=0.9} = 0.33 \pm 0.11$ and $b_{z=0.9} = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts. \\

The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=9.8$ is $\simeq0.05$ dex beneath the KROSS relation at the same mass.
The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}. 
We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$.

@@

After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.

@@

In the right panel of Figure \ref{fig:tf_relation} we plot the mean and median values and percentiles of the $V_{C}$ distribution for the comparison and KDS isolated field samples, finding wide $V_{C}$ distributions which reflect the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear. \\

In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e. the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).

The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, much closer to the $\left<V_{C}\right> = 95kms^{-1}$ lower limit.
This implies that the observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contribute to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
This topic is discussed further throughout \cref{sec:discussion}. \\

@@

In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$.

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}
\usepackage{enumitem}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{enumitem}

@@

\newcommand{\Sers}{S\'{e}rsic }
\newcommand{\Lagr}{\mathcal{L}}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: ojamesturner@icloud.com (OJT)}}$
M. Cirasuolo,$^{2,1}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: 
\begin{enumerate}[label=(\roman*),align=left]
\item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes?
\item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?
\end{enumerate}

This paper focuses on the first question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work. \\

@@

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
Most of the galaxies for the KMOS observations had a confirmed spectroscopic redshift (see below).
A subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
In each pointing, few sources had no spectroscopic redshift and were selected on the basis of their photometric redshift.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).

@@

Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focus of UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from a set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$, {\it HK}-band $R\simeq2000$).
\subsubsection{Observations}\label{subsubsec:Obs}

@@

To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the {\it K}-band greatly reduces the sky-line residuals. 
We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
The PSF was determined by fitting the collapsed {\it K}-band image of the stacked control stars in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack. \\

@@

To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening. \\

@@

\begin{enumerate}[label=(\roman*),align=left]
\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
\item $\frac{S}{N_{m}} > 3$
\end{enumerate}

@@

The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all (8/9) of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
The 32/38 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.

@@

Throughout the following sections we analyse the derived kinematic parameters of the isolated field sample, placing the galaxies in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in Appendix \ref{app:comparison_samples}.
In Appendix \ref{app:comparison_samples} we describe our careful assessment of lower redshift samples from the literature, using tabulated data where possible to re-compute mean and median $V_{C}$ and $\sigma_{int}$ values.
These fair comparisons help to disentangle true evolution in the kinematic properties of typical star-forming galaxies from systematic effects originating in disparate measurement techniques or galaxy selection criteria.
During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{tully_fisher_standard_log.png}
    \end{subfigure} \hspace{0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{v_evolution.png}
    \end{subfigure}
    \caption{{\it Left:} We plot log($V_{C}$) vs. log($M_{\star}/M_{\odot}$) for the isolated field sample, with the rotation-dominated galaxies in red and dispersion-dominated galaxies with the hollow symbols.
    We also plot with the solid green line the $z\simeq0.9$ relation recovered from a fit to $\simeq400$ rotation-dominated galaxies from the KROSS survey \protect\cite{Harrison2017}, with the shaded region showing the associated $\simeq$0.2 dex scatter on the fit.
    This $z\simeq0.9$ relation shows no signifcant evolution from the fit to a local sample of spiral galaxies with $z < 0.1$, presented in \protect\cite{Reyes2011}.
    The rotation-dominated KDS galaxies, and galaxies classed as reliable from the AMAZE survey \protect\citep{Gnerucci2011}, also show no evolution from this relation within the scatter, with the dispersion-dominated galaxies scattering below the relation.
    This highlights the need for careful sample selection when constructing this relation.
    {\it Right:} The mean, median and distributions of the comparison sample $V_{C}$ measurements are plotted against redshift.
    The symbol positions with black errorbars (some not visible) show the mean values and the horizontal filled and grey bars show the median values and associated errors, and the mean mass of each survey (in units of log($M_{\star}/M_{\odot}$)) is listed beside the survey name.
    Note that the median errors for the AMAZE Clean sample are shaded orange to avoid confusion with the full sample.
    The $V_{C}$ distributions in each of the individual studies are wide, reflecting the galaxy diversity within each sample.
    The low mean value of $V_{C}$ in the KDS isolated field sample is driven mainly by averaging over a sample which contains a higher fraction of dispersion-dominated galaxies with lower rotation velocities.}
    \label{fig:tf_relation}
\end{figure*}

@@

We plot the relationship between rotation velocity and stellar mass for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ star-forming galaxies with $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a_{z=0.9} = 0.33 \pm 0.11$ and $b_{z=0.9} = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
In \cite{Reyes2011}, $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts.

The rotation-dominated KDS isolated field sample galaxies are broadly consistent within the scatter with the $z\simeq0.9$ relation, but with a tendency to lie below the relation.
When considered alone, the mean velocity of the rotation-dominated isolated field sample galaxies ($V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$) at their mean mass of $log(M_{\star}/M_{\odot})=9.8$ is $\simeq0.05$ dex beneath the KROSS relation at the same mass.
The dispersion-dominated KDS galaxies sit clearly separated and below the $z\simeq0.9$ relation, bringing significant scatter to lower $V_{C}$ values at fixed $M_{\star}$ as is also observed in $z\simeq0.9$ dispersion-dominated galaxies and for early-type galaxies in the local universe \citep[e.g.][]{Romanowsky2012}. 
We plot also the five galaxies from the AMAZE Clean ($z\simeq3$) sample, which are consistent within the scatter with the relation for typical star-forming galaxies at $z\simeq0.9$. \\

@@

@@

With the KDS, we have added the largest sample of galaxies observed with integral-field spectroscopy at $z>3$, and with our simple $V_{C}/\sigma_{int} > 1$ cut we conclude that the stellar mass Tully-Fisher relation defined for rotation-dominated star-forming galaxies appears to show no evolution between $z\simeq0.1$ and $z\simeq3.5$.
However, as we will show in \cref{subsec:rdf_v_over_sigma}, the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.
We also explore this in the context of the mean rotation velocities of the comparison samples throughout the following subsection.

@@

The right panel of Figure \ref{fig:tf_relation} indicates that the $V_{C}$ distributions for the comparison and KDS isolated field samples are wide, reflecting the mass range and the mixture of rotation/dispersion-dominated galaxies which constitute the samples.
The isolated field sample mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$.
However, the mean and median rotation velocity of the rotation dominated galaxies are $V_{C} = 96.7^{+7.3}_{-7.2}kms^{-1}$ and $V_{C} = 93.0^{+8.1}_{-7.7}kms^{-1}$ respectively, suggesting that averaging over a sample containing a large number of dispersion dominated galaxies is bringing the averages down.

It is difficult to assess whether the $V_{C}$ values reported in the comparison samples (the modelling and extraction techniques differ as described in Appendix \ref{app:comparison_samples}) are directly comparable.
The MASSIV, KROSS, KMOS$^{3D}$ and KDS samples should in principle yield comparable $V_{C}$ values which rely on extracting from the data at a fiducial radius or using a velocity shear value, but the comparison to the dynamical models of SINS and AMAZE is not so clear.
Despite the wide distributions, the comparison samples generally have higher mean rotation velocities. \\

In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e. the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=9.8$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $95kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of the gas mass and dark matter mass would raise this estimate).
This value is above the mean and median values of the isolated field sample, but comparable to the mean and median of the rotation dominated galaxies, suggesting that rotation in these systems could support at most the stellar mass of the galaxy.

As mentioned above, the observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
However, it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contribute to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
This topic is discussed further throughout \cref{sec:discussion}. \\

@@

In the right panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the fractional error weighted mean, median and distributions of $\sigma_{int}$ from the comparison and KDS isolated field samples.
The values increase sharply from $\sigma_{int}\simeq10-20kms^{-1}$ as traced by $z\simeq0$ measurements of typical SFGs to $\sigma_{int}\simeq30-60kms^{-1}$ at $z\simeq1$ to $\sigma_{int}\simeq40-90kms^{-1}$ at $z\simeq3$, but with a wide range of values observed at each redshift.
There appears to be a trend for the surveys with lower average stellar mass (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) to have higher velocity dispersions than the surveys with larger average stellar mass (GHASP, KMOS$^{3D}$, SINS).
